---
title: "Colors"
author: "Mark Gallivan"
date: ""
output: 
  md_document:
    variant: markdown_github
---

```{r setup}
library(RColorBrewer)
library(data.table)

# color parameter options:  c("greys","blues","reds","greens","oranges","purples")
getSeqColors <- function(color, N) {
  colorRefDat <- data.table(colorSelect = 
                              c("greys","blues","reds","greens","oranges","purples"), minCol = c("grey0","lightskyblue","indianred1","darkseagreen1","goldenrod1","lavender"), maxCol = 
                              c("grey100","blue4","darkred","darkgreen","darkorange3","purple4"))
  
  shades <- colorRampPalette(c(colorRefDat[colorSelect == color]$minCol, 
                               colorRefDat[colorSelect == color]$maxCol))
  returnColors <- shades(N)
  return(returnColors)
}

getQualColors <- function(n) {
qual_col_pals = brewer.pal.info[brewer.pal.info$category == 'qual',]
col_vector = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, 
rownames(qual_col_pals)))
return(col_vector)
}

```

## The Problem

I have a use case of showing many colors on the same graph. Many existing palettes are constrained to 8 or 12 colors. For example, R Color Brewer (RColorBrewer::display.brewer.all()) has palettes with only 10-12 colors.

I would like an easy function that provides me with a unique palette of colors that are either sequential (c("light blue","blue","dark blue")) or categorical or qualitative (c("red","white","blue")).

For more information on types of color palettes see http://colorbrewer2.org/learnmore/schemes_full.html

## The Solution 

Now let's to do a test for the sequential color palette. 

```{r Sequential}

## Sequential 
colorVec <- getSeqColors("reds",20)
getSeqColors("reds",20)
mat <- matrix(rep(1:20, each = 20))
image(mat, axes = FALSE, col = colorVec)

```

Now let's to do a test for the categorical or qualitative color palette. 

```{r Categorical}
colorVecQual <- getQualColors(n = 20)
colorVecQual
mat <- matrix(rep(1:20, each = 20))
image(mat, axes = FALSE, col = colorVecQual)


```

